Manuscript title here

### 2021-07-02 doc/ms/ms.Rmd
updated text and new percentile analysis and figure for measuring the likelihood of skewness.

| Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980]. Taxon-specific secondary production estimates were combined with
diet proportions, diet-specific assimilation efficiencies, *AE~i~*, and assumed net production efficiencies, *NPE*, to estimate consumption of organic matter. For each food
category, *i*, diet proportions were multiplied by the gross growth efficiency ($GGE_{i} = AE_{i} * NPE$) to calculate the relative production attributable to each food
category. The relative production from each food type was then multiplied by the interval-level production and finally divided by $GGE_{i}$ to estimate consumption of organic
matter from each food category by a consumer [@benke1980]. Consumption was calculated for each taxon across sampling intervals (typically \~1 month). Total interval consumption was
calculated by summing across all taxa, while annual consumption was calculated by summing across all taxa and intervals. Variability in consumption estimates was estimated through
a Monte Carlo approach, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and consumption estimated with
the TBP method using modeled diet proportions (see *Diet analysis* above), diet-specific assimilation efficiencies, and net production efficiency. Variability in *AE~i~* was
incorporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36),
filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants
(bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968; @cross2007; @cross2011; @benke1980; @benke1997]. Variability in *NPE* was
incorporated by resampling values from an assumed beta distribution with median *NPE* = 0.45 (95% PI = 0.4-0.5). Beta distributions were fit using the 'get.beta.par()' function
within the *rriskDistributions* package [@belgorodski2017].

@@

| To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes, such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ... p_S$. The Lorenz curve plots how a value, in this
case OM flux, accumulates with increasing cumulative proportion of species. In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is
simply a straight diagonal line. Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$
[@solomon1975; @chao2019]: $$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$

@@

We were interested in how OM fluxes were distributed (randomly vs. non-randomly) in relation to species traits (i.e., body size, $P:B$ ratio, population biomass) across the temperature gradient. We used a permutation analyses to test for non-random patterns in OM flux with species traits. First, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$). We then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:

@@

where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution. To determine the probability of observing the skewness we observe in the data compared to random ordering, we constructed a distribution of skewness estimates from random species ordering while maintaining the relative distribution of OM fluxes. The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$), therefore we permuted 1,000,000 random species orderings and calculating the skew in the cumulative distribution of annual OM fluxes. We then use this random distribution to estimate the probability of observing a skewness as extreme or greater.

@@

| Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020]. Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` -- `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature. Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)` [`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$.

@@

Generally, the material fluxes within a stream were distributed unequally among consumers, however, this varied among streams (Figure 1; Figure S1). The calculated inequality, i.e. Gini coefficient, ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`]; Table 1). Differences in inequality were partly attributed to consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers. Patterns of material fluxes were still unequally distributed among consumers even after correcting for differences in species richness (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`]; Table 1).

@@

Unequal distributions of fluxes within streams corresponded to very different patterns in dominance of OM fluxes across streams (Figure 1a). For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species (`r round(n_dom_min$dom_flux,2)`% to `r round(n_dom_max$dom_flux,2)`% of flux, respectively). Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblages within streams. Differences in dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences along the temperature gradient.

@@

>>>>

Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980]. Taxon-specific secondary production estimates were combined with
diet proportions, diet-specific assimilation efficiencies, *AE~i~*, and assumed net production efficiencies, *NPE*, to estimate consumption of organic matter. For each food
category, *i*, diet proportions were multiplied by the gross growth efficiency ($GGE_{i} = AE_{i} * NPE$) to calculate the relative production attributable to each food
category. The relative production from each food type was then multiplied by the interval-level production and finally divided by $GGE_{i}$ to estimate consumption of organic
matter from each food category by a consumer [@benke1980]. Consumption was calculated for each taxon across sampling intervals (typically \~1 month). Total interval consumption was
calculated by summing across all taxa, while annual consumption was calculated by summing across all taxa and intervals. Variability in consumption estimates was estimated through
a Monte Carlo approach, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and consumption estimated with
the TBP method using modeled diet proportions (see *Diet analysis* above), diet-specific assimilation efficiencies, and net production efficiency. Variability in *AE~i~* was
incorporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36),
filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants
(bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968; @cross2007; @cross2011; @benke1980; @benke1997]. Variability in *NPE* was
incorporated by resampling values from an assumed beta distribution with median *NPE* = 0.45 (95% PI = 0.4-0.5). Beta distributions were fit using the 'get.beta.par()' function
within the *rriskDistributions* package [@belgorodski2017].

@@

To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes, such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ... p_S$. The Lorenz curve plots how a value, in this
case OM flux, accumulates with increasing cumulative proportion of species. In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is
simply a straight diagonal line. Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$
[@solomon1975; @chao2019]: $$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$

@@

We were interested in the question of how temperature may select for certain species traits (i.e., body size, $P:B$ ratio, population biomass) and therefore OM fluxes would skew towards populations with those traits. To detect this, for all bootstrapped estimates of annual OM flux, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$) and then calculated a measure of skewness, $Sk_{flux}$, based on quartiles of the distribution of OM fluxes in relation to species traits as:

@@

where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution. To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [i.e., feasible set; @haegeman2008;], given the number of species and the relative distribution of energy fluxes within a community. The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings). Therefore, we chose to permute a portion of each stream community's feasible set by randomly ordering species and calculating the skewness in the cumulative distribution of annual OM fluxes 100,000 times. The number of random orderings was chosen as a balance between characterizing the relative distribution of skewness values within each feasible set and computational and time constrains. This permuted set allowed us to calculate the likelihood of observing the empirical skewness, $Sk_{flux}$, in each stream. Further, we estimated the

@@

Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020]. Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` -- `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` -- `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature. Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)` [`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`--`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$.

@@

Generally, OM fluxes were distributed unevenly among consumers, however, the extent varied among streams (Figure 1; Figure S1). Gini inequality coefficients ranged from `r gini_summary %>% select('Non.normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>% select(Non.normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>%  select('Non.normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Non.normalized.Gini_mean) %>% select('Non.normalized.Gini_quant97.5') %>% round(2)`]; Table 1). Differences in inequality were partly attributed to variation in consumer species richness among streams which ranged from `r spp_richness %>% select(taxon_n) %>% min` to `r spp_richness %>% select(taxon_n) %>% max` consumers. Yet, even after accounting for differences in consumer richness,patterns of material fluxes were still unevenly distributed among consumers (Normalized Gini coefficient: `r gini_summary %>% select('Normalized.Gini_mean') %>% min %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>% select(Normalized.Gini_quant2.5) %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_min(Normalized.Gini_mean) %>%  select('Normalized.Gini_quant97.5') %>% round(2)`] to `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>%  select('Normalized.Gini_mean') %>% round(2)` [`r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant2.5') %>% round(2)` -- `r gini_summary %>% data.frame %>% dplyr::slice_max(Normalized.Gini_mean) %>% select('Normalized.Gini_quant97.5') %>% round(2)`]; Table 1).

@@

Variation in the relative distribution of OM fluxes among consumers corresponded to different patterns of dominance across streams (Figure 1a). For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species (`r round(n_dom_min$dom_flux,2)`% to `r round(n_dom_max$dom_flux,2)`% of flux, respectively). Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblages within streams. Differences in dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences along the temperature gradient.

@@

[@diaz2021] SAD are more uneven than their statistical background

### 2021-07-02 doc/ms/tables-figures.Rmd
updated text and new percentile analysis and figure for measuring the likelihood of skewness.

---
title: ""
author: "Report Author"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   word_document:
     reference_docx: docx_template.docx
   pdf_document:
     keep_tex: true
   html_document: default
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \linenumbers
linestretch: 1
---

@@

Figure 3. Histograms of species trait distributions of (a) log~10~ annual production:biomass ratio (y^-1^), (b) log~10~ mean body mass (mg ind^-1^), and (c) log~10~ annual mean population biomass (mg m^-2^).

@@

Figure 4. Relative cumulative fluxes among species in relation to ranked order of (a) annual production:biomass ratio (y^-1^) and (b) mean body size (mg ind^-1^).

```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
drake::loadd(lorenz_trait_fig)
grid.arrange(lorenz_trait_fig[["pb_lorenz_flux_plot"]], lorenz_trait_fig[["M_lorenz_flux_plot"]], ncol = 2, bottom = textGrob("Cumulative relative species", vjust = 1, gp = gpar(fontfamily = 'serif')),
                         left = textGrob("Cumulative relative flux", rot = 90, vjust = 1, gp = gpar(fontfamily = 'serif')))

@@

Figure 4. Bootstrapped distribution of skew statistics from OM fluxes with body size, *M*, and (b) population annual production:biomass ratio relative to the distribution of skew statistics of 100,000 random orderings.

```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE}
drake::loadd(random_skew_fig)
grid.arrange(random_skew_fig[[1]], random_skew_fig[[2]], ncol = 1)

@@

>>>>

---
title: ""
author: "JR Junker"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   word_document:
     reference_docx: docx_template.docx
   pdf_document:
     keep_tex: true
   html_document: default
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \linenumbers
linestretch: 1
---

@@

Figure 2. Histograms of species trait distributions of (a) log~10~ mean body mass (mg ind^-1^), (b) log~10~ annual production:biomass ratio (y^-1^), and (c) log~10~ annual mean population biomass (mg m^-2^).

@@

Figure 3. Relative cumulative fluxes among species in relation to ranked order of (a) mean body size (mg ind^-1^) and (b) annual production:biomass ratio (y^-1^).

```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
drake::loadd(lorenz_trait_fig)
grid.arrange(lorenz_trait_fig[["M_lorenz_flux_plot"]], lorenz_trait_fig[["pb_lorenz_flux_plot"]], ncol = 2, bottom = textGrob("Cumulative relative species", vjust = 1, gp = gpar(fontfamily = 'serif')),
                         left = textGrob("Cumulative relative flux", rot = 90, vjust = 1, gp = gpar(fontfamily = 'serif')))

@@

Figure 4. Fluxes of organic matter were skewed along gradients of the population traits (a) mean individual body size, *M*, and (b) annual population production:biomass, *P:B* ratiopopulation traits. Percentile Density of empirical skewness of OM fluxes in relation to .  relative to the distribution of skew statistics of 100,000 random orderings.

```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE}
drake::loadd(random_skew_fig)
grid.arrange(random_skew_fig[["M_perc_plot"]], random_skew_fig[["pb_perc_plot"]], ncol = 1, left = text_grob(""))

@@

Figure S4.

### 2021-07-02 docs/ms/ms.RMD
updated text and new percentile analysis and figure for measuring the likelihood of skewness.

### Evenness Among consumers

To visualize and quantify how evenly OM fluxes were distributed among consumers within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes,
such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ... p_S$. The Lorenz curve plots how a value, in this
case OM flux, accumulates with increasing cumulative proportion of species. In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is
simply a straight diagonal line. Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$
[@solomon1975; @chao2019]: $$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$

@@

We were interested in how OM fluxes were distributed (randomly vs. non-randomly) in relation to species traits (i.e., body size, $P:B$ ratio, population biomass) across the temperature gradient. We used a permutation analyses to test for non-random patterns in OM flux with species traits. First, we ordered species based on within-stream ranking of annual population traits (i.e, $M$, $P:B$) and measured the asymmetry in the distribution of annual OM flux with species traits. To determine the probability of observing the empirical asymmetry we constructed a random distribution of asymmetry values. The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$), therefore chose to permute estimated this by randomly ordering species 10,000,000 times and calculating the skew in the cumulative distribution of annual OM fluxes. We then use this random distribution to estimate the probability of observing

>>>>

### Evenness of production among consumers

To visualize and quantify how evenly OM fluxes were distributed throughout consumes within a stream, we constructed Lorenz curves [@lorenz1905] on ordered relative consumption fluxes,
such that in a community with $S$ species and the relative consumption of species *i*, $p_i$, is ordered $p_1 \leq p_2 \leq ... p_S$. The Lorenz curve plots how a value, in this
case OM flux, accumulates with increasing cumulative proportion of species. In a community with perfectly equal distribution of OM consumption among species, the Lorenz curve is
simply a straight diagonal line. Deviation from perfect equality was calculated as the Gini coefficient [@gini1921], normalized for differences in $S$ among streams, $G^*$
[@solomon1975; @chao2019]: $$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$

@@
